Compare pseqs

### 2019-10-04 comparepseqs.Rmd
MC

```{R models}
ret <- list()

for (key in names(rds)) {
    pseq.species <- import_filter_data(rds[[key]],
                               included = c("MEN", "BL_AGE", "SYSTM", "DIASM", "BMI",
                                            "CURR_SMOKE", "BL_USE_RX_C09",
                                            "Q57X", "BL_USE_RX_C03",
                                            "BL_USE_RX_C07", "BL_USE_RX_C08"))

@@

    g4 <- plot.diversities(diversities)
    ggsave(file = sprintf("cache/comparepseqs-%s.png", key), plot=g4, height=6, width=9)
}
```

>>>>

```{R models}
mclapply(c2l(names(rds)), function(key) {
    pseq.species <- import_filter_data(rds[[key]],
                               included = c("MEN", "BL_AGE", "SYSTM", "DIASM", "BMI",
                                            "CURR_SMOKE", "BL_USE_RX_C09",
                                            "Q57X", "BL_USE_RX_C03",
                                            "BL_USE_RX_C07", "BL_USE_RX_C08"))

@@

    g4 <- plot.diversities(diversities)
    ggsave(file = sprintf("cache/comparepseqs-%s.png", key), plot=g4, height=6, width=9)
}, mc.cores = length(rds))
```
